Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-05 paper/paper.tex
Expanded on edited the proposal section

\begin{abstract}
Tabnabbing is a phishing technique that attempts to change the look and design of a tab when the user is not currently viewing it so that when the user returns, they will find a seemingly trustworthy form or page requesting their credentials and information.  
This attack utilizes the user's trust of recently viewed tabs, and the perceived immutability of out-of-focus tabs.
Tabnabbing attacks change the appearance of tabs by using JavaScript or the HTML meta tag.  
Previous attempts of addressing tabnabbing have relied upon detecting tabnabbing after it has occurred.  
Detecting whether a page has changed with the malicious intent of tabnabbing is a complex problem that is difficult to solve without large amounts of processing or false positives.  
The authors of this paper investigated and developed a preemptive measure to prevent tabnabbing attacks from occurring.  
The resulting Chrome browser extension, Nabi, prevents any JavaScript or HTML meta tags from running in inactive tabs outside of a trusted whitelist.
\end{abstract}

@@

\section{Proposal and Methodology}
\begin{comment}
Each of these approaches has advantages and disadvantages, but one particular disadvantage all these methods possess is that they are all only detection programs. We believe that a preventative method is a more effective way to combat tabnabbing.
We propose a web browser extension to prevent attackers from executing their tabnabbing attacks. Aza Raskin suggested the use of the NoScript add-on for the Firefox web browser to eliminate the use of JavaScript across all tabs in the browser.  Our proposed system is similar to this approach, but is implemented in the Google Chrome web browser and differs from Raskin’s proposed solution in some key elements. Unlike NoScript, which blocks all javascript across every tab within a browser window, our extension will block javascript specifically in all non-active tabs that are not part of a trusted whitelist.  
\end{comment}
Each of these proposed approaches has particular advantages and disadvantages, but all of them require that the tabnabbing attack be detected first and then dealt with by the software or by alerting the user. Our proposed solution takes a preventative approach to stopping tabnabbing attacks. Aza Raskin suggested the use of the NoScript add-on for the Firefox web browser to eliminate the use of JavaScript across all tabs in the browser. Our proposed system, Nabi, is similar to this approach, but is implemented as an extension in the Google Chrome web browser and differs from Raskin’s proposed solution in some key elements. Unlike NoScript, which blocks all javascript across every tab within a browser window, our extension will block javascript specifically in all non-active tabs.

Our proposal is the prevent all tabnabbing attacks by restricting their ability to execute within the browser. Since tabnabbing attacks inherently run when the user is not looking, our solution is to prevent their execution whenever the user is not viewing that tab. If the attack occurs while the user is looking at the page, they will hopefully notice the change and avoid having their personal data phished by the newly created website. More so, since the active tab is allowed to run javascript, it gives the user the ability to still navigate to and utilize pages that incorporate javascript functionality, unlike Raskin's NoScript suggestion. This can be circumvented via a whitelist feature for both active and inactive tabs, and will be added as a future feature in Nabi.

The primary aspects of Nabi are as follows: Javascript restriction and allowance system, whitelisting of trusted domains, and the detection and prevention of scriptless redirect attacks.

\section{Results}
The current build of Nabi restricts javascript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running javascript on that page. The page that is switched to is given access to run javascript and is also refreshed to reflect the change in permissions. This prevents javascript in the unactive from running while the user is not viewing it, but allows it to reactivate once the user returns.

The only two forms of tabnabbing are through javascript and via the scriptless HTML meta tag redirect. Our system currently only prevents the former of the two types of attack, but prevents this attack completely. Previous approaches must be able to detect an active attack and take necessary action, and thus can be circumvented if the attacker is aware of the method's metrics of detection. Nabi can provably prevent all javascript tabnabbing attacks before they ever occur by restricting their access to execute only when the user has that tab focused.

>>>>

\begin{abstract}

\end{abstract}

@@

\section{Proposal and Methodology}
\begin{comment}
Each of these approaches has advantages and disadvantages, but one particular disadvantage all these methods possess is that they are all only detection programs. We believe that a preventative method is a more effective way to combat tabnabbing.
We propose a web browser extension to prevent attackers from executing their tabnabbing attacks. Aza Raskin suggested the use of the NoScript add-on for the Firefox web browser to eliminate the use of JavaScript across all tabs in the browser.  Our proposed system is similar to this approach, but is implemented in the Google Chrome web browser and differs from Raskin’s proposed solution in some key elements. Unlike NoScript, which blocks all JavaScript across every tab within a browser window, our extension will block JavaScript specifically in all non-active tabs that are not part of a trusted whitelist.  
\end{comment}
Each of these proposed approaches has particular advantages and disadvantages, but all of them require that the tabnabbing attack be detected first and then dealt with by the software or by alerting the user. Our proposed solution takes a preventative approach to stopping tabnabbing attacks. Aza Raskin suggested the use of the NoScript add-on for the Firefox web browser to eliminate the use of JavaScript across all tabs in the browser. Our proposed system, Nabi, is similar to this approach, but is implemented as an extension in the Google Chrome web browser and differs from Raskin’s proposed solution in some key elements. Unlike NoScript, which blocks all JavaScript across every tab within a browser window, our extension will block JavaScript specifically in all non-active tabs.

Our proposal is to prevent all tabnabbing attacks by restricting their ability to execute within the browser. Since tabnabbing attacks inherently run when the user is not looking, our solution is to prevent their execution whenever the user is not viewing that tab. If the attack occurs while the user is looking at the page, they will hopefully notice the change and avoid having their personal data phished by the newly created website. As such, the active tab is allowed to run JavaScript, and thus the user still has the ability to navigate to and utilize pages that incorporate JavaScript functionality, unlike Raskin's NoScript suggestion which blocks all untrusted sources from running JavaScript.

The primary aspects of Nabi are as follows: a JavaScript permissions system, a system for whitelisting trusted domains, and a system for the detection and prevention of scriptless redirect attacks. The permissions system will dynamically allow and deny access rights of JavaScript as the user navigates tabs. This system could be implemented a number of ways, such as removing JavaScript tags from the page or changing the access rights of tab, but should inevitably strive to prevent any JavaScript execution. The whitelist provides the user with a way to maintain productivity while staying protected. The user may select trusted websites to be exempt from being blocked by the system, allowing that page to continue running JavaScript after the user has changed tabs. Lastly, the system must provide a method for handling scriptless attacks. The scriptless attack cannot detect when the user selects a different tab, so it must guess the expected time a user will spend looking at their page in order to redirect to the alternative site when they are presumably looking elsewhere. Thus the system must detect when a meta tag is used to issue a redirect request to the browser and either prevent it from doing so or informing the user that the redirect will be occurring.

\section{Results}
The current build of Nabi restricts JavaScript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running JavaScript on that page. The page that is switched to is given access to run JavaScript and is also refreshed to reflect the change in permissions. This prevents JavaScript in the unactive from running while the user is not viewing it, but allows it to reactivate once the user returns.

The only two forms of tabnabbing are through JavaScript and via the scriptless HTML meta tag redirect. Our system currently only prevents the former of the two types of attack, but prevents this attack completely. Previous approaches must be able to detect an active attack and take necessary action, and thus can be circumvented if the attacker is aware of the method's metrics of detection. Nabi can provably prevent all JavaScript tabnabbing attacks before they ever occur by restricting their access to execute only when the user has that tab focused.
